A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\medskip
Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the PCA-LinReg Case, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation. The limits of the techniques used for the PCA-LinReg Case will be discussed in the author's future work.

Before going on to review the results of the simulations, it is beneficial to briefly consider the Buckley-Leverett and cross-flow behaviour which are be used to validate the results from this work.

>>>>

\medskip
Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the PCA-LinReg Case, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation. The limits of the techniques used for the PCA-LinReg Case will be discussed in future work.

\medskip
Before discuss flow simulation results with permeability distribution resulted from methods described in Sections~\ref{subsection:pcspaces} and \ref{subsection:model}), it is beneficial to briefly consider the Buckley-Leverett flow model and cross-flow behaviour which are used to validate the results from this work.
